---
title: "Untitled"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(RSelenium)
library(XML)
library(rvest)
library(stringr)
library(knitr)
library(dplyr)
library(tidyr)
library(lubridate)
library(httr)
library(readxl)
library(writexl)
library(jsonlite)
library(kableExtra)
library(DT)
library(readr)
library(xml2)
library(ggplot2)
library(plotly)
library(dygraphs)
library(quantmod)
library(shiny)
library(tigris)
library(highcharter)
library(netstat)

free.port <- netstat::free_port(random=TRUE)

rD <- rsDriver(browser="firefox", port = free.port, chromever=NULL)
remDr <- rD$client

now <- Sys.time()
today <- format(Sys.time(), "%Y%m%d")

## 팟빵 에피소드 수집 함수 선언
podbbang <- function(channel.id) {
  
  URL <- str_c("http://www.podbbang.com/_m_api/podcasts/", channel.id, "/episodes?offset=0&sort=pubdate:desc&episode_id=0&limit=8&with=summary&cache=0")
  
  txt <- readLines(URL, warn=FALSE)
  
  df <- fromJSON(txt)$data %>% 
    select(published_at, title, duration)
  
  names(df) <- c("date", "title", "duration")
  
  df$date <- df$date %>% 
    as.Date() %>% 
    format("%y.%m.%d")
  
  df$title <- df$title %>% 
    str_remove_all("^[0-9]{2}/[0-9]{2} -") %>% 
    str_trim()
  
  return(df)
  
}


## Naver News Keyword Search
naver.news.api.search <-function(keyword) {
  
searchUrl <- "https://openapi.naver.com/v1/search/news.xml"
client_id <- "M4g9rW2aSU0zNVXbp0Ve"
client_secret <- "gfr6xh20HF"

search.word <- keyword
query <- search.word %>% 
  enc2utf8() %>% 
  URLencode()

url <- str_c(searchUrl, "?query=", query, "&display=20")

res <- GET(url, 
           add_headers("X-Naver-Client-Id"=client_id, 
                       "X-Naver-Client-Secret"=client_secret))
doc <- toString(res)

xmlFile <- xmlParse(doc)
xmlRoot(xmlFile)
df <- xmlToDataFrame(getNodeSet(xmlFile, "//item"), stringsAsFactors = FALSE)
  
}

# Emission Price
setwd("C:/Users/Minkyung Lee/Desktop/QAE/final")

emission.price.down <-function(todate) {
gen_otp_url = 'https://ets.krx.co.kr/contents/COM/GenerateOTP.jspx'
gen_otp_data = list(
    name= "fileDown",
    filetype= "csv",
    url= "ETS/03/03010000/ets03010000_05",
    isu_cd= "KRD050032204",
    fromdate= "20220612",
    todate= todate,
    pagePath= "/contents/ETS/03/03010000/ETS03010000.jsp")

otp = POST(gen_otp_url, query = gen_otp_data) %>% read_html() %>% html_text()
  
down_url = 'https://file.krx.co.kr/download.jspx'
down_eprice = POST(down_url, query = list(code = otp), add_headers(referer = gen_otp_url)) %>% read_html(encoding = 'UTF-8') %>%  html_text() %>% read_csv()
}

```

Emission Price Board
================================================================================================

Row {data-heigth=300}
------------------------------------------------------------------------------------------------
### Today's Emission Price {.value-box}
```{r}
todate1 <- today
chart1 <- emission.price.down(todate1)
nowprice <- chart1[1,6]

valueBox(
    value = nowprice,
    icon = "fa-area-chart",
    color = "primary")

```

### KAU22 Trading Price 
```{r}
chart1 <- emission.price.down(todate1)
Price.date <- chart1$일자 %>% as.Date()
Price.now <- chart1$시가
volume.now <- chart1$거래량
p = ggplot(chart1) +
  geom_line(aes(x=Price.date,y=Price.now),group = 1 , col ='red') +
  geom_point(aes(x=Price.date,y=Price.now), col ='red')
ggplotly(p)

``` 

### KAU22 Trading Volume
```{r}
todate1 <- today
chart1 <- emission.price.down(todate1)
Price.date <- chart1$일자 %>% as.Date()
Price.now <- chart1$시가
volume.now <- chart1$거래량

p2 <- ggplot(chart1) +
  geom_bar(aes(x = Price.date, y = volume.now), stat = "identity", fill = "royalblue") +
  geom_point(aes(x = Price.date, y = volume.now), col = 'royalblue') +
  xlab("Date") + ylab("Trading volume")
ggplotly(p2)
```


Row {data-heigth=300} 
------------------------------------------------------------------------------------------------

### Today's Trading Volume {.value-box}
```{r}

chart1 <- emission.price.down(todate1)
nowvolume <- chart1[1,9]

valueBox(
    value = nowvolume,
    icon = "fa-area-chart",color = 'royalblue')
```

### KAU22 Price Table

```{r}
todate1 <- today
chart1 <- emission.price.down(todate1)
 
DT::datatable(chart1, fillContainer = TRUE)

```

Row {data-heigth=400} 
------------------------------------------------------------------------------------------------

### The Status of Today's emission price
```{r}
todate1 <- today
chart1 <- emission.price.down(todate1)
nowprice <- chart1[1,6]
peakvalue <- max(chart1$"고가")
rating=nowprice/peakvalue*100
rating.value <- rating %>% round(1) %>% as.numeric()

gauge(rating.value, min = 0, max = 100, gaugeSectors(
  success = c(70.0, 100.0), warning = c(40.0, 69.9), danger = c(0, 39.9)
))
```

### News Articles: Emission Trading Scheme
    
```{r}
keyword <- "배출권 거래제"
query2 <- keyword
tab2 <- naver.news.api.search(query2)
tab2 <- cbind(query2, tab2) 
tab2 <- tab2 %>% select(-originallink, -description)
tab2 <- tab2 %>% 
    mutate(pubDate = str_remove(pubDate, " \\d{2}:.+")) %>% 
    mutate(title = str_replace_all(title, "&quot;", '"'))

names(tab2) <- c("Search", "Title", "Link", "Date")

df2 <- tab2 %>%
  mutate(Title = cell_spec(Title, "html", link = Link, color="#062872")) %>% 
  select(Date, Search, Title)

df2 %>% 
  kable(escape=FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "30em")
```

### News Articles: Emission Price
    
```{r}
keyword <- "배출권 가격"
query <- keyword
tab <- naver.news.api.search(query)
tab <- cbind(query, tab) 
tab <- tab %>% select(-originallink, -description)
tab <- tab %>% 
    mutate(pubDate = str_remove(pubDate, " \\d{2}:.+")) %>% 
    mutate(title = str_replace_all(title, "&quot;", '"'))

names(tab) <- c("Search", "Title", "Link", "Date")

df <- tab %>%
  mutate(Title = cell_spec(Title, "html", link = Link, color="#062872")) %>% 
  select(Date, Search, Title)

df %>% 
  kable(escape=FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "30em")
```

Certified Emission Board
================================================================================================

Row {data-heigth=300}
------------------------------------------------------------------------------------------------
### Number of Covered Entities in 2022 {.value-box}

```{r}
setwd("C:/Users/Minkyung Lee/Desktop/QAE/final")
download.file("https://etrs.gir.go.kr/home/infoOpen/infoOpenList9Excel.do?pagerOffset=0&maxPageItems=10&maxIndexPages=10&searchKey=&searchValue=&menuId=20&condition.plPeriDgr=3&condition.infoOpenYn=Y&condition.pfYy=2022&csvYn=Y", "data.csv")
emission_dt <- read.csv("data.csv", fileEncoding = "EUC-KR")
numenti <- nrow(emission_dt)

valueBox(
  value = nowprice,
  icon = "fa-area-chart",
  color = "primary")

```

### Certified Emission by Sector

```{r}
setwd("C:/Users/Minkyung Lee/Desktop/QAE/final")
download.file("https://etrs.gir.go.kr/home/infoOpen/infoOpenList9Excel.do?pagerOffset=0&maxPageItems=10&maxIndexPages=10&searchKey=&searchValue=&menuId=20&condition.plPeriDgr=3&condition.infoOpenYn=Y&condition.pfYy=2022&csvYn=Y", "data.csv")
emission_dt <- read.csv("data.csv", fileEncoding = "EUC-KR")
p1 <- plot_ly(emission_dt, labels = ~부문, values = ~인증배출량, type = "pie")
p1


```

### News Articles: Net-Zero Scenario
    
```{r}
keyword <- "탄소중립"
query2 <- keyword
tab2 <- naver.news.api.search(query2)
tab2 <- cbind(query2, tab2) 
tab2 <- tab2 %>% select(-originallink, -description)
tab2 <- tab2 %>% 
    mutate(pubDate = str_remove(pubDate, " \\d{2}:.+")) %>% 
    mutate(title = str_replace_all(title, "&quot;", '"'))

names(tab2) <- c("Search", "Title", "Link", "Date")

df2 <- tab2 %>%
  mutate(Title = cell_spec(Title, "html", link = Link, color="#062872")) %>% 
  select(Date, Search, Title)

df2 %>% 
  kable(escape=FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "30em")
```


Row {data-heigth=300}
------------------------------------------------------------------------------------------------

### Total Certified Emission in 2022 {.value-box}

```{r}
setwd("C:/Users/Minkyung Lee/Desktop/QAE/final")
download.file("https://etrs.gir.go.kr/home/infoOpen/infoOpenList9Excel.do?pagerOffset=0&maxPageItems=10&maxIndexPages=10&searchKey=&searchValue=&menuId=20&condition.plPeriDgr=3&condition.infoOpenYn=Y&condition.pfYy=2022&csvYn=Y", "data.csv")
emission_dt <- read.csv("data.csv", fileEncoding = "EUC-KR")
totalemit <- sum(emission_dt$인증배출량)

valueBox(
    value = totalemit,
    icon = "fa-area-chart",
    color = "primary")
```

### The Company emitting highest GHG emission {.value-box}

```{r}
setwd("C:/Users/Minkyung Lee/Desktop/QAE/final")
download.file("https://etrs.gir.go.kr/home/infoOpen/infoOpenList9Excel.do?pagerOffset=0&maxPageItems=10&maxIndexPages=10&searchKey=&searchValue=&menuId=20&condition.plPeriDgr=3&condition.infoOpenYn=Y&condition.pfYy=2022&csvYn=Y", "data.csv")
emission_dt <- read.csv("data.csv", fileEncoding = "EUC-KR")
maxcomp <- emission_dt %>% filter(인증배출량 == max(인증배출량))
company_name <- maxcomp$업체명

valueBox(
    value = company_name,
    icon = "fa-area-chart",
    color = "primary")

```

### Certified Emission Table

```{r}
setwd("C:/Users/Minkyung Lee/Desktop/QAE/final")
download.file("https://etrs.gir.go.kr/home/infoOpen/infoOpenList9Excel.do?pagerOffset=0&maxPageItems=10&maxIndexPages=10&searchKey=&searchValue=&menuId=20&condition.plPeriDgr=3&condition.infoOpenYn=Y&condition.pfYy=2022&csvYn=Y", "data.csv")
emission_dt <- read.csv("data.csv", fileEncoding = "EUC-KR")
emission_dt <- emission_dt[,-1]
 
DT::datatable(emission_dt, fillContainer = TRUE)

```

Research
=====================================     

Row 
-------------------------------------
### Potcasts: 듣다보면 똑똑해지는 라디오
Potcasts Link: https://www.podbbang.com/channels/9213

```{r}

podbbang <- function(channel.id) {
  
  URL <- str_c("https://app-api6.podbbang.com/channels/", channel.id, "/episodes?offset=0&limit=20&sort=desc&episode_id=0")
  txt <- readLines(URL, warn=FALSE)
  
  df <- fromJSON(txt)$data 
  df1 <- df %>%
    select(publishedAt, title)
  df2 <- df$media %>% 
    select(duration, url)
  df <- cbind(df1, df2)
  
  names(df) <- c("date", "title", "duration", "link")
  
  df$date <- df$date %>% as.Date() %>% format("%y.%m.%d")
  
  df$title <-str_replace_all(df$title, "^[0-9]{2}/[0-9]{2} -", "") %>% str_trim()
  
  return(df)
  
}
channel.id=9213 
tbl <- podbbang(channel.id)
df <- tbl %>%
  mutate(title.link = cell_spec(title, "html", link = link, color="#062872")) %>%
  select(date, title.link, duration)
df %>% head(12) %>%
  kable(format="html", escape=FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(1, width = "6em") %>%
  column_spec(2, width = "35em") %>%
  column_spec(3, width = "6em")


```

### Youtube: 최재천의 아마존
Youtube link: https://www.youtube.com/@choemazon/videos

```{r, include=FALSE}
URL <- "https://www.youtube.com/@choemazon/videos"
remDr$navigate(URL)
Sys.sleep(3)
txt <- remDr$getPageSource()[[1]]
res <- read_html(txt)
title <- res %>%
  html_nodes("#video-title") %>%
  html_text() %>% 
  str_remove("\n") %>% 
  str_trim() %>% 
  .[1:length(.)-1]
link <- res %>%
  html_nodes("#video-title-link") %>%
  html_attr("href") %>%
  .[1:length(.)-1] %>% 
  str_c("https://www.youtube.com", .)
date <- res %>% 
  html_nodes("#metadata-line > span:nth-child(4)") %>% 
  html_text()
length <- res %>%
  html_nodes("#overlays > ytd-thumbnail-overlay-time-status-renderer > span") %>%
  html_text() 
tbl <- cbind(date, title, length, link) %>%
  as.data.frame(stringsAsFactors=FALSE)
df <- tbl %>%
  mutate(title.link = cell_spec(title, "html", link = link, color="#062872")) %>%
  select(date, title.link, length)
names(df) <- c("Date", "Title", "Length")
```

```{r}
df %>% head(30) %>%
  kable(format="html", escape=FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(1, width = "6em") %>%
  column_spec(2, width = "35em") %>%
  column_spec(3, width = "6em")
```

Row {.tabset .tabset-fade}
-------------------------------------
    
### Ted talks: Energy
Ted Link: https://www.ted.com/talks?sort=newest&topics%5B%5D=energy

```{r}

URL <- str_c("https://www.ted.com/talks?sort=newest&topics%5B%5D=energy")
res <- read_html(URL)

# speaker
pattern <- ".talk-link__speaker"
speaker <- res %>% 
    html_nodes(pattern) %>%
    html_text()

# posted date
pattern <- ".meta__val"
posted <- res %>%
    html_nodes(pattern)%>%
    html_text() %>%
    str_trim()

  # duration
pattern <- ".thumb__duration"
duration <- res %>%
    html_nodes(pattern) %>%
    html_text()

  # titles
pattern <- ".f-w\\:700 .ga-link"
title <- res %>%
  html_nodes(pattern) %>%
  html_text() %>% 
    str_trim()

  # link
pattern <- ".f-w\\:700 .ga-link"
link <- res %>%
    html_nodes(pattern) %>% 
    html_attr("href") %>% 
    str_c("https://www.ted.com/", .)

tbl2 <- cbind(posted, title, duration, link) %>% as.data.frame()
dk <- tbl2 %>%
  mutate(title.link = cell_spec(title, "html", link = link, color="#062872")) %>%
  select(posted, title.link, duration)
dk %>% head(25) %>%
  kable(format="html", escape=FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(1, width = "6em") %>%
  column_spec(2, width = "35em") %>%
  column_spec(3, width = "6em")

  
```

### Google Scholar: Emission Price 

```{r, include=FALSE}
Stack <- NULL
pagelist <- c(0,10,20,30)
for(i in pagelist){
  URL <- str_c("https://scholar.google.com/scholar?start=",i,"&q=emission+price&hl=en&as_sdt=0,5&as_ylo=2019")
  res <- read_html(URL)

## title
pattern <- ".gs_rt a"
title2 <- res %>% 
  html_nodes(pattern) %>% 
  html_text()


pattern <- ".gs_a"
citation2 <- res %>% 
  html_nodes(pattern) %>% 
  html_text() %>% str_remove(" - .*") 


  ##link
pattern <- ".gs_rt a"
link2 <- res %>% 
  html_nodes(pattern) %>% 
  html_attr("href")

tbl3 <- cbind(title2, citation2, link2) %>% as.data.frame()

Stack <- rbind(Stack, tbl3)
  
  Sys.sleep(1)
  
}

```

```{r}
dk <- Stack %>%
  mutate(title.link = cell_spec(title2, "html", link = link2, color="#062872")) %>%
  select(title.link,citation2)

dk %>% head(40) %>%
  kable(format="html", escape=FALSE) %>%
  kable_styling(bootstrap_options = c("hover", "condensed")) %>%
  column_spec(1, width = "20em") %>%
  column_spec(2, width = "20em")
```

